---
title: "JA bid paper analyses"
author: "Gideon Salter and Malinda Carpenter"
date: "`r Sys.Date()`"
output: html_document
---

```{r Load packages, warning=FALSE, message=FALSE}
library(readr) #Read data file from GitHub
library(tidyverse) #Data manipulation
library(reshape2) #Data manipulation
library(lme4) #Fitting GLMMs
library(MuMIn) #Model comparison
library(emmeans) #Conduct posthoc comparisons
library(sjPlot) #Print tables of coefficients
library(performance) #Check for overdispersion in GLMs/GLMMs
library(vcd) #Visualise distribution of data (here, for count outcome variable)
library(irr) #Calculating inter-rater reliability
```

## Read in data
Data from public Github repository (https://github.com/g-salter/ja_bid_study_data/)

```{r Read data, message=FALSE}
data <- read_csv(url("https://raw.githubusercontent.com/g-salter/ja_bid_study_data/main/ja_bid_data.csv?token=GHSAT0AAAAAACIIW6VX3XZOWDEZ5T7BQX72ZKBOKOQ")) 
data <- as_tibble(data)
data$age_days_cen <- scale(data$age_days, center = TRUE, scale = FALSE)
data <- data %>% relocate(age_days_cen, .after = participant)

```

## 1. Analysis of combined data from all tasks (free play and three behavioural tests)
The first set of models examine whether infants' age predicts whether they produce a communicative look across all of the four tasks used in the study.  

```{r Combined}
# Create new variable with highest value across all 4 tasks
data_2 <- data %>% 
  mutate(highscore_all = (pmax(int_sight, int_sound, moving_toy, freeplay, na.rm = TRUE)))
    
# Build models
model_all1 <- glm(highscore_all ~ age_days_cen + as.factor(participant), family = binomial(link = "logit"), data = data_2)
model_all2 <- glmer(highscore_all ~ age_days_cen + (1|participant), family = binomial(link = "logit"), data = data_2)
model_all3 <- glmer(highscore_all ~ as.factor(age_months) + (1|participant),family = binomial(link = "logit"),data = data_2)

# Model selection
model.sel(model_all1, model_all2, model_all3)
summary(model_all2)
confint(model_all2)
    
# Posthoc comparisons on age using model with age as factor
posthoc_all <- emmeans(model_all3, revpairwise~age_months, adjust="Tukey")
summary(posthoc_all$contrasts)
confint(posthoc_all$contrasts)

# Tables of coefficients
tab_model(model_all2, show.se = TRUE)
tab_model(model_all3, show.se = TRUE)
    
```    

## 2. Analysis of data from free play
The second set of models examine whether infants' age predicts whether they produce a communicative look during free play.

```{r Free play}
# Build Models
model_fp1 <- glm(freeplay ~ age_days_cen + as.factor(participant), family = binomial(link = "logit"), data = data)
model_fp2 <- glmer(freeplay ~ age_days_cen + (1|participant), family = binomial(link = "logit"), data = data)
model_fp3 <- glmer(freeplay ~ as.factor(age_months) + (1|participant), family = binomial(link = "logit"), data = data)
  
# Model selection
model.sel(model_fp1, model_fp2, model_fp3)
summary(model_fp2)
confint(model_fp2)
    
# Posthoc comparisons on age using model with age as factor
posthoc_fp <- emmeans(model_fp3, revpairwise ~ age_months, adjust="Tukey")
summary(posthoc_fp$contrasts)
confint(posthoc_fp$contrasts)

# Tables of coefficients
tab_model(model_fp2, show.se = TRUE)
tab_model(model_fp3, show.se = TRUE)
```
    
## 3. Data from behavioural tests
The third set of models examine whether infants' age predicts whether they produce a communicative look during the three behavioural tests.
    
```{r Behavioural tests}    
# Create new variable with highest value across the 3 behavioural tasks
data_3 <- data %>%
          mutate(highscore_bt = (pmax(int_sight, int_sound, moving_toy, na.rm = TRUE)))
    
# Build models
model_tests1 <- glm(highscore_bt ~ age_days_cen + as.factor(participant), family = binomial(link = "logit"), data = data_3)
model_tests2 <- glmer(highscore_bt ~ age_days_cen + (1|participant), family = binomial(link = "logit"), data = data_3)
model_tests3 <- glmer(highscore_bt ~ as.factor(age_months) + (1|participant), family = binomial(link = "logit"), data =      data_3)
    
# Model selection
model.sel(model_tests1, model_tests2, model_tests3)
summary(model_tests2)
confint(model_tests2)
    
# Posthoc comparisons on age using model with age as factor
posthoc_tests <- emmeans(model_tests3, revpairwise ~ age_months, adjust="Tukey")
summary(posthoc_tests$contrasts)
confint(posthoc_tests$contrasts)
    
# Tables of coefficients
tab_model(model_tests2, show.se = TRUE)
tab_model(model_tests3, show.se = TRUE)
```

## 4. Data split into experimental tests versus free play
The fourth set of models examine whether infants' age and type of task (free play or behavioural test, combining the three tests) predict whether they produce a communicative look.

```{r Experimental vs free play}
# Create new longform dataset
data_3 <- data %>%
          mutate(highscore_bt = (pmax(int_sight, int_sound, moving_toy, na.rm = TRUE)))
data_4 <- data_3 %>% select (c(participant, age_days_cen, freeplay, highscore_bt))
data_long_1 <- melt(data_4, id = c("participant", "age_days_cen"))
data_long_1 <- as_tibble(data_long_1)
names(data_long_1) <- c("participant", "age_days_cen", "type", "score")

#For categorical age
data_5 <- data_3 %>% select (c(participant, age_months, freeplay, highscore_bt))
data_long_2 <- melt(data_5, id = c("participant", "age_months"))
data_long_2 <- as_tibble(data_long_2)
names(data_long_2) <- c("participant", "age_months", "type", "score")
    
# Build models
model_testfp1 <- glm(score ~ age_days_cen + as.factor(participant) + type, family = binomial(link = "logit"), data = data_long_1)
model_testfp2 <- glmer(score ~ age_days_cen + type + (1|participant), family = binomial(link = "logit"), data = data_long_1)
model_testfp3 <- glmer(score ~ as.factor(age_months) + type + (1|participant), family = binomial(link = "logit"), data = data_long_2)
    
# Model selection
model.sel(model_testfp1, model_testfp2, model_testfp3)
summary(model_testfp2)
confint(model_testfp2)
    
# Posthoc comparison on type
posthoc_testfp <- emmeans(model_testfp2, revpairwise ~ type, adjust="Tukey")
summary(posthoc_testfp$contrasts)
confint(posthoc_testfp$contrasts)

# Tables of coefficients
tab_model(model_testfp2, show.se = TRUE)
tab_model(model_testfp3, show.se = TRUE)
    
# Build models with age*task type interaction
model_testfp3 <- glm(score ~ age_days_cen*type + as.factor(participant), family = binomial(link = "logit"), data = data_long_1)
model_testfp4 <- glmer(score ~ age_days_cen*type + (1|participant), family = binomial(link = "logit"), data = data_long_1)
model_testfp5 <- glmer(score ~ as.factor(age_months)*type + (1|participant), family = binomial(link = "logit"), data = data_long_2)

# Model selection
model.sel(model_testfp3, model_testfp4, model_testfp5)
summary(model_testfp4)
    
# Posthoc comparisons on type for each level of age (using model with age as factor)
posthoc_testfp2 <- emmeans(model_testfp5, revpairwise ~ type|age_months, adjust="Tukey")
summary(posthoc_testfp2$contrasts)
confint(posthoc_testfp2$contrasts)

# Tables of coefficients
tab_model(model_testfp4, show.se = TRUE)
tab_model(model_testfp5, show.se = TRUE)

```

## 5. Data split by each task type, including the three behavioural tests and free play
The fifth set of models examine whether infants' age and type of task (free play or three behavioural tests) predict whether they produce a communicative look.

```{r All tasks separate}
# Create new longform dataset with continuous age (days)
data_6 <- data %>% select(c(participant, age_days_cen, freeplay, int_sight, int_sound, moving_toy))
data_long_3 <- melt(data_6, id = c("participant", "age_days_cen"))
data_long_3 <- as_tibble(data_long_3)
names(data_long_3) <- c("participant", "age_days_cen", "type", "score")

# Create new longform dataset for categorical age (months)
data_7 <- data %>% select (c(participant, age_months, freeplay, int_sight, int_sound, moving_toy))
data_long_4 <- melt(data_7, id = c("participant", "age_months"))
data_long_4 <- as_tibble(data_long_4)
names(data_long_4) <- c("participant", "age_months", "type", "score")
 
# Build models
model_ts1 <- glm(score ~ age_days_cen + type + as.factor(participant), family = binomial(link = "logit"), data = data_long_3)
model_ts2 <- glmer(score ~ age_days_cen + type + (1|participant), family = binomial(link = "logit"), data = data_long_3)
model_ts3 <- glmer(score ~ as.factor(age_months) + type + (1|participant), family = binomial(link = "logit"), data = data_long_4)
    
# Model selection
model.sel(model_ts1, model_ts2, model_ts3)
summary(model_ts2)
    
# Posthoc comparisons on type
posthoc_ts <- emmeans(model_ts2, pairwise~type, adjust="Tukey")
summary(posthoc_ts$contrasts)
confint(posthoc_ts$contrasts)

# Confidence intervals for significant differences
confint(posthoc_ts$contrasts)

# Tables of coefficients
tab_model(model_ts2, show.se = TRUE)
```

## 6. Counts of JA production by task
The sixth set of models examine whether infants' age predicts the number of different tasks in which they produce a communicative look.

```{r Counts}
# Create new count variable based on number of tasks in which participant produces a JA bid 
data_counts <- data %>%
mutate(count_score = (int_sight + int_sound + moving_toy + freeplay))
    
# Check distribution and fit of count data
distplot(data_counts$count_score, type="poisson")
fit <- goodfit(data_counts$count_score, type="poisson")
summary(fit) 
    
# Build models
model_count1 <- glm(count_score ~ age_days_cen + as.factor(participant), family = poisson, data = data_counts)
model_count2 <- glmer(count_score ~ age_days_cen + (1|participant), family = poisson(link = "log"), data = data_counts)
model_count3 <- glmer(count_score ~ as.factor(age_months) + (1|participant), family = poisson(link = "log"), data = data_counts)
    
# Check for overdispersion
check_overdispersion(model_count1)
check_overdispersion(model_count2)
check_overdispersion(model_count3)

# Model selection
model.sel(model_count1, model_count2, model_count3)
summary(model_count2)
confint(model_count2)

# Posthoc comparisons on age using model with age as factor
posthoc_count <- emmeans(model_count3, revpairwise~age_months, adjust="Tukey")
summary(posthoc_count$contrasts)
confint(posthoc_count$contrasts)

# Tables of coefficients
tab_model(model_count2, show.se = TRUE)
tab_model(model_count3, show.se = TRUE)

```
## 7. Percentage of cases in which communicative looks were followed by a gaze shift back to the stimulus

```{r Gaze shifts back}
# Bids with looks back to stimulus in Interesting Sight task
interesting_sight_bids_gs <-  sum(na.omit(data$int_sight_gs))
total_interesting_sight_bids <- sum(na.omit(data$int_sight))
(interesting_sight_bids_gs/total_interesting_sight_bids) * 100

# Bids with looks back to stimulus in Moving Toy task
moving_toy_bids_gs <-  sum(na.omit(data$moving_toy_gs))
total_moving_toy_bids <- sum(na.omit(data$moving_toy))
(moving_toy_bids_gs/total_moving_toy_bids) * 100

# Bids with looks back to stimulus in Free Play
freeplay_bids_gs <-  sum(na.omit(data$freeplay_gs))
total_freeplay_bids <- sum(na.omit(data$freeplay))
(freeplay_bids_gs/total_freeplay_bids) * 100

#Overall bids with looks back to stimulus
overall_gs <- interesting_sight_bids_gs + moving_toy_bids_gs + freeplay_bids_gs
overall_bids <- total_interesting_sight_bids + total_moving_toy_bids + total_freeplay_bids
(overall_gs/overall_bids) * 100


```


## 8. Reliability
```{r Reliability, message=FALSE}
#Read in data
reliability_data <- read_csv(url("https://raw.githubusercontent.com/g-salter/ja_bid_study_data/main/ja_bid_reliability.csv?token=GHSAT0AAAAAACIIW6VWHRN2DMIFQ65BPG3CZKBOE7A")) 

#Initial reliability and agreement for all tasks combined (experimental tests and free play)
ratings <- reliability_data[,4:5]

kappa2(ratings, "squared")
agree(ratings)

#Initial reliability and agreement for behavioural tests
reliability_data_b <- reliability_data %>% filter(type != "freeplay")
ratings_b <- reliability_data_b[,4:5]

kappa2(ratings_b, "squared")
agree(ratings_b)

#Initial reliability and agreement for free play
reliability_data_fp <- reliability_data %>% filter(type == "freeplay")
ratings_fp <- reliability_data_fp[,4:5]

kappa2(ratings_fp, "squared")
agree(ratings_fp)


```
